Regularized target encoding outperforms traditional methods in supervised machine learning with high cardinality features

### 2021-04-30 publication/manuscript.Rmd
fix figure 5

```{r, rank-res, out.height=".55\\textwidth", fig.cap='(ref:rank-res)', out.width="\\textwidth"}
plotdt = rbindlist(lapply(names(cons_list), function(x) {
  r = relation_class_ids(cons_list[[x]][[1]])
  data.frame(method = names(r), rank = r, algorithm = x)
}))
set(plotdt, which(plotdt$method == "remove" & plotdt$algorithm == "RF"), "rank", 11)
plotdt = plotdt[-which(plotdt$method == "none"),]
plotdt$method = factor(plotdt$method,
 levels = c("integer", "frequency", "dummy", "one-hot", "hash", "leaf", "impact",
    "glmm-noCV", "glmm-5CV", "glmm-10CV", "remove")
)
plotdt[, lab := method]
swit = Vectorize(function(x) {
  switch(x,
  "frequency" = "frq",
  "one-hot" = "oh",
  "remove" = "rm",
  "integer" = "int",
  "dummy" = "dumm",
  "leaf" = "leaf",
  "impact" = "imp",
  "glmm-10CV" = "CV10",
  "glmm-5CV" = "CV5",
  "glmm-noCV" = "noCV",
  "hash" = "hash"
)})
levels(plotdt$lab) = unlist(swit(levels(plotdt$method)))

>>>>

```{r, rank-res, out.height=".55\\textwidth", fig.cap='(ref:rank-res)', out.width="\\textwidth", message = FALSE}
plotdt = rbindlist(lapply(names(cons_list), function(x) {
  r = relation_class_ids(cons_list[[x]][[1]])
  data.frame(method = names(r), rank = r, algorithm = x)
}))
set(plotdt, which(plotdt$method == "remove" & plotdt$algorithm == "RF"), "rank", 11)
plotdt = plotdt[-which(plotdt$method == "none"),]
plotdt$method = factor(plotdt$method,
 levels = c("integer", "frequency", "dummy", "one-hot", "hash", "leaf", "impact",
    "glmm-noCV", "glmm-5CV", "glmm-10CV", "remove")
)
plotdt[, lab := method]
swit = Vectorize(function(x) {
  switch(x,
  "frequency" = "frq",
  "one-hot" = "oh",
  "remove" = "rm",
  "integer" = "int",
  "dummy" = "dumm",
  "leaf" = "leaf",
  "impact" = "imp",
  "glmm-10CV" = "CV10",
  "glmm-5CV" = "CV5",
  "glmm-noCV" = "noCV",
  "hash" = "hash"
)})
levels(plotdt$lab) = unlist(swit(levels(plotdt$method)))
